The Effect of Void on the

### 2018-10-04 draft/alexpub.tex
add new

% Full title of the paper (Capitalized)
% \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha$($\rm Ti_3Al$) Alloy}
\Title{The Effect of Void on the}
% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Fracture processes of nanocrystalline metallic materia is affected by dislocation, nanovoid and other defects. Existing studies of defect evolution in titanium-aluminium alloy cover the case that voids located in single crystals, inside grain in poly crystals and at the grain boundaries.Molecular dynamics simulation was performed to study the evolution of a spherical nanovoid in $\alpha$+$\gamma$ two-phase titanium-aluminium alloy under uniaxial tension. The results show that voids located at the $\alpha$/$\gamma$ phase boundary have significant detract to strength of Ti-Al polycrystalline.}

% Keywords
\keyword{$\alpha$ + $\gamma$ two phase TiAl alloy; void; molecular dynamics}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\bibliography{ref/VIOLET-ref.bib}

@@

\cite{}
$\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure \cite{}, and $\alpha TiAl$ is hcp structure, the structure of the two initial cells are shown in Fig.\cite{}, and the constructing parameters are givin by Table.\cite{}. The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure \cite{}. Periodic boundary conditions (PBC)are applied along all three directions, that makes poly crystal with periodic nanovoid structures. The initial dimension of simulation cell is  $L_x = $ nm, $L_y = $ nm, $L_z = $ nm, and each model contains about 4.6 million atoms. The grain orientation and size were randomly created with Voronoi method with code ATOMSK \cite{}, and resulting in the arbitrary shape and orientation of the grains. Only one spherical void defect was placed intragranularlly or intergranularlly within each simulation model void within each simulation model. The intragranular spherical void was located in grain interior of the largest grain of the simulation model, as shown in Fig. \cite{}. The intergranular spherical void was at the center of the simulation cell, as shown in Fig. \cite{}.

@@

	\section{Results and Discussion}
%	/home/alex/Documents/violet/draft/img/perfect-line.pdf

	\begin{figure}[ht]
		\centering
		\includegraphics[width=1\linewidth]{img/perfect-line2-2}
		\caption{perfect-line2-2}
		\label{fig:perfect-line2-2}
	\end{figure}

	\begin{table}[ht]
		\caption{Key point during tensile process}
		\centering
		\begin{tabular}{l c c c c c c c c c c}
		\toprule
		 \textbf{Key Number} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{9} & \textbf{10}\\
		\midrule
		Time/ps	& 0 & 0.15 & 0.16 & 0.17 & 0.18 & 0.19 & 0.20 & 0.21 & 0.22 & 0.23 \\
		\midrule
		Strain	& 0 & 0.15 & 0.16 & 0.17 & 0.18 & 0.19 & 0.20 & 0.21 & 0.22 & 0.23 \\
		\bottomrule
		\end{tabular} 
		\label{tab:key-pint}
	\end{table}

\subsection{Deformation Behaviour of Two Phase Alloys without Void Defects}
However, the following discussion concentrates on deformation phenomena that rely on the elastoplastic codeformation of the $\gamma$ and $\gamma_2$ phases and on the particular point defect situation occurring in twophase alloys. Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
\begin{figure}[ht]
		\centering
		\includegraphics[width=1\linewidth]{img/def-gamma}
		\label{fig:def-gamma}
		\caption{$\gamma$ phase deformation}
\end{figure}
The configure of atoms is shown in Fig.\ref{fig:yield}, it can be seen that dislication emission initiate in $\gamma$ pahse in XXX ps, and the deformation canbe mainly confied to the majority $\gamma$ pahse. $\gamma$(TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2<110] and superdislocations with the Burgers vectors b=<101] and $b=1/2<11\overline{2}]$. The other potential deformation mode is mechanical twinning along $1/6<11\overline{2}]{111}$.
From Fig.\ref{fig:yield}, of the two constituents of ($\alpha_2$+$\gamma$) alloys, the $\alpha_2$ phase is more difficult to deform. A reason for the unequal strain partitioning between the $\alpha_2$ and $\gamma$ phase is certainly the strong plastic anisotropy of the $\alpha_2$ phase. TEM examinations performed on tensile  tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is mainly carried by local slip of <a>-type dislocations with the Burgers vector $b=1/3<11\overline{2}0>$ prism planes\ref{fig:yield}, which is by far the easiest slip system in $\alpha_2$ single crystals. 
	\begin{figure}[ht]
		\centering
		\includegraphics[width=1\linewidth]{img/def-alpha}
		\label{fig:def-alpha}
		\caption{$\alpha$ phase deformation}
	\end{figure}
Basic deformationg mechanism of $\alpha$ phase

	\begin{figure}[ht]
		\centering
		\includegraphics[width=1\linewidth]{"img/disl-gamma"}
		\caption{Disloaction in $\gamma$}
		\label{fig:dis-alpha}
	\end{figure}

@@

The core of  a dislocation intersecting an interface often needs to be transformed. For example, an ordinary 1/2<110] dislocation gliding in one $\gamma$ grain has to be converted in to a <101] super dislocation with the double Burgers vector gliding in an adjacent $\gamma$ grain. At the $\alpha/\gamma$ interface the dislocations existing in the $D0_{19}$ structure have to be transformed into dislocations consistent with the $L1_0$structure. These core transformations are associated with a change of the dislocation line energy because the lengths of the Burgers vectors and the shear module are different.

@@

Void of R=10$\AA$ was placed at phase boundary, inside $\alpha$ phase grain respectively. Effect of void at different position under uniaxial tension is shown in Fig.\ref{fig:stress&strain}. The strength of materails with void in different size and at different position is shown in Fig.\ref{fig:stress&strain}. The results show that the model without void defect has best stength, while the void loacted inside $\alpha$ phase detracts the strength of the material most, and the void at the phase boundary have less impact on the strength.

@@

	%\begin{figure}[ht]
	%	\centering
	%	\includegraphics[width=0.7\linewidth]{img/allline}
	%	\caption{Fracture process of specimen with void in $\alpha$ phase}
	%	\label{ }
	%\end{figure}
	%

>>>>

% Full title of the paper (Capitalized)
% \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha_2$($\rm Ti_3Al$) Alloy}
\Title{The Effect of Void on the}
% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Fracture processes of nanocrystalline metallic materia is affected by dislocation, nanovoid and other defects. Existing studies of defect evolution in titanium-aluminium alloy cover the case that voids located in single crystals, inside grain in poly crystals and at the grain boundaries.Molecular dynamics simulation was performed to study the evolution of a spherical nanovoid in $\alpha_2$+$\gamma$ two-phase titanium-aluminium alloy under uniaxial tension. The results show that voids located at the $\alpha_2$/$\gamma$ phase boundary have significant detract to strength of Ti-Al polycrystalline.}

% Keywords
\keyword{$\alpha_2$ + $\gamma$ two phase TiAl alloy; void; molecular dynamics}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

@@

\cite{}
$\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure \cite{}, and $\alpha_2 TiAl$ is hcp structure, the structure of the two initial cells are shown in Fig.\cite{}, and the constructing parameters are givin by Table.\cite{}. The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure \cite{}. Periodic boundary conditions (PBC)are applied along all three directions, that makes poly crystal with periodic nanovoid structures. The initial dimension of simulation cell is  $L_x = $ nm, $L_y = $ nm, $L_z = $ nm, and each model contains about 4.6 million atoms. The grain orientation and size were randomly created with Voronoi method with code ATOMSK \cite{}, and resulting in the arbitrary shape and orientation of the grains. Only one spherical void defect was placed intragranularlly or intergranularlly within each simulation model void within each simulation model. The intragranular spherical void was located in grain interior of the largest grain of the simulation model, as shown in Fig. \cite{}. The intergranular spherical void was at the center of the simulation cell, as shown in Fig. \cite{}.

@@

\section{Results and Discussion}
%	/home/alex/Documents/violet/draft/img/perfect-line.pdf
In order to examine deforamtion behaviour carefully, tensile loading was applied to the model without any types of void defect. The whole tension process was saperated into four stages: Stage-1 is typical elasttic part of the deformation, which is originated from $\epsilon = 0$ to $\epsilon = 0.092$, includeing key point 1. Stage-2 is yield stage ranging from $\epsilon = 0.092$ to $\epsilon = 0.101$, including key points 2 to 6. In stage-2, the stress decreased slightly along with the increasing of strain. Stage-3 is cracking stage and in this stage the strength of the model have beeen was detracted sharply, we can confine that the structure almost fail after the stage-3. Snapshots of atoms configuration are labeled with key points number from 1 to 10, specific list of key points numbers were shown in Table.\ref{tab:key-point}. Deformation beaviour of the $\alpha_2$ phase had $\gamma$ phase were discussed in the folling subsection respectively.

	\begin{figure}[ht]
		\centering
		\includegraphics[width=1\linewidth]{img/perfect-line2-2}
		\caption{Deformation process of the model without void defect}
		\label{fig:deformation-pf}
	\end{figure}

	\begin{table}[ht]
		\caption{Key point during tensile process}
		\centering
		\begin{tabular}{l c c c c c c c c c c}
		\toprule
		 \textbf{Key Number} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{9} & \textbf{10}\\
		\midrule
		Time/ps	& 0 & 0.15 & 0.16 & 0.17 & 0.18 & 0.19 & 0.20 & 0.21 & 0.22 & 0.23 \\
		\midrule
		Strain	& 0 & 0.092 & 0.094 & 0.096 & 0.099 & 0.101 & 0.104 & 0.107 & 0.110 & 0.112 \\
		\bottomrule
		\end{tabular} 
		\label{tab:key-point}
	\end{table}

\subsection{Deformation Behaviour of Two Phase Alloys without Void Defects}
However, the following discussion concentrates on deformation phenomena that rely on the elastoplastic codeformation of the $\gamma$ and $\gamma_2$ phases and on the particular point defect situation occurring in twophase alloys. Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
\begin{figure}[ht]
		\centering
		\includegraphics[width=1\linewidth]{img/def-gamma}
		\label{fig:def-gamma}
		\caption{$\gamma$ phase deformation}
\end{figure}
The configure of atoms is shown in Fig.\ref{fig:yield}, it can be seen that dislication emission initiate in $\gamma$ pahse in XXX ps, and the deformation canbe mainly confied to the majority $\gamma$ pahse. $\gamma$(TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2<110] and superdislocations with the Burgers vectors b=<101] and $b=1/2<11\overline{2}]$. The other potential deformation mode is mechanical twinning along $1/6<11\overline{2}]{111}$.
From Fig.\ref{fig:yield}, of the two constituents of ($\alpha_2$+$\gamma$) alloys, the $\alpha_2$ phase is more difficult to deform. A reason for the unequal strain partitioning between the $\alpha_2$ and $\gamma$ phase is certainly the strong plastic anisotropy of the $\alpha_2$ phase. TEM examinations performed on tensile  tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is mainly carried by local slip of <a>-type dislocations with the Burgers vector $b=1/3<11\overline{2}0>$ prism planes\ref{fig:yield}, which is by far the easiest slip system in $\alpha_2$ single crystals. 
	\begin{figure}[ht]
		\centering
		\includegraphics[width=1\linewidth]{img/def-alpha}
		\label{fig:def-alpha_2}
		\caption{$\alpha_2$ phase deformation}
	\end{figure}
Basic deformationg mechanism of $\alpha_2$ phase

	\begin{figure}[ht]
		\centering
		\includegraphics[width=1\linewidth]{"img/disl-gamma"}
		\caption{Disloaction in $\gamma$}
		\label{fig:dis-alpha_2}
	\end{figure}

@@

The core of  a dislocation intersecting an interface often needs to be transformed. For example, an ordinary 1/2<110] dislocation gliding in one $\gamma$ grain has to be converted in to a <101] super dislocation with the double Burgers vector gliding in an adjacent $\gamma$ grain. At the $\alpha_2/\gamma$ interface the dislocations existing in the $D0_{19}$ structure have to be transformed into dislocations consistent with the $L1_0$structure. These core transformations are associated with a change of the dislocation line energy because the lengths of the Burgers vectors and the shear module are different.

@@

Void of R=10$\AA$ was placed at phase boundary, inside $\alpha_2$ phase grain respectively. Effect of void at different position under uniaxial tension is shown in Fig.\ref{fig:stress&strain}. The strength of materails with void in different size and at different position is shown in Fig.\ref{fig:stress&strain}. The results show that the model without void defect has best stength, while the void loacted inside $\alpha_2$ phase detracts the strength of the material most, and the void at the phase boundary have less impact on the strength.

@@

	%\begin{figure}[ht]
	%	\centeringT
	%	\includegraphics[width=0.7\linewidth]{img/allline}
	%	\caption{Fracture process of specimen with void in $\alpha_2$ phase}
	%	\label{ }
	%\end{figure}
	%
